\documentclass[10pt, a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=0.75in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}
\usepackage{array}
\usepackage{booktabs}
\setlength{\parindent}{0pt}
\renewcommand{\familydefault}{\sfdefault}

\hypersetup{
    colorlinks=true,
    urlcolor=blue,
    linkcolor=black,
}

\begin{document}

\begin{center}
    \Huge\textbf{TAN YU HANG} \\[6pt]
    \normalsize
    Mobile: 86140868 \quad 
    Email: \href{mailto:tanyuhang.tyh.tyh@gmail.com}{tanyuhang.tyh.tyh@gmail.com} \quad 
    GitHub: \href{https://github.com/gnahuy123}{github.com/gnahuy123} \\
    LinkedIn: \href{https://www.linkedin.com/in/tan-yu-hang/}{linkedin.com/in/tan-yu-hang-350189363} \quad 
    Website: \href{https://www.gnahuy123.github.io}{gnahuy123.github.io}
\end{center}

\vspace{10pt}
\hrule
\vspace{10pt}

\section*{EDUCATION}
\vspace{-5pt}
\textbf{National University of Singapore} \hfill \textbf{Aug 2024 – Dec 2027} \\
Bachelor of Computing in Computer Science, minor in Mathematics and Statistics \\
GPA: 4.7/5 (First Class Honours) \\
\textit{Relevant Modules:} Discrete Structures (A), Programming Methodology I (A+), Programming Methodology II (A), \\
Linear Algebra for Computing (A), Probability and Statistics (A), Data Structures and Algorithms (A-), \\
Software Engineering (A-), Computer Organisation (A-)

\vspace{10pt}
\section*{SKILLS}
\begin{itemize}[noitemsep, leftmargin=*]
    \item \textbf{Programming Languages:} Python (Proficient), Java (Proficient), JavaScript/TypeScript (Proficient), C (Working), SQL (Proficient), HTML/CSS (Working)
    \item \textbf{Frontend:} React (Vite), React Native (Expo)
    \item \textbf{Backend:} Node.js, Express.js, FastAPI
    \item \textbf{Databases:} MySQL, Supabase, PostgreSQL
    \item \textbf{Testing/Other:} JUnit, JavaFX
\end{itemize}

\vspace{10pt}
\section*{WORK EXPERIENCE}
\vspace{-5pt}
\textbf{ECICS} \hfill \textbf{Jan 2026 – Present} \\
\textit{Full Stack Developer Intern}
\begin{itemize}[noitemsep, leftmargin=*]
    \item Optimised Robotic Process Automation to improve error rate.
    \item Refactored 2000 lines of code from legacy systems.
    \item Built UiPath Python Robotic Process Automation to improve speed and accuracy with legacy systems.
\end{itemize}

\vspace{5pt}
\textbf{NUS School of Computing} \hfill \textbf{May 2025 – Dec 2025} \\
\textit{Teaching Assistant – CS1101S}
\begin{itemize}[noitemsep, leftmargin=*]
    \item Conducted weekly 2-hour tutorial sessions, reinforcing core CS concepts and mentoring problem-solving skills.
    \item Achieved 5.0/5.0 Teaching Feedback score (4.3 department average) with 83\% response rate and 60\% teaching award nomination.
    \item Evaluated $\sim$20 student coding assignments weekly ($\sim$100 lines each) without automated tests, requiring deep code comprehension.
\end{itemize}

\vspace{5pt}
\textbf{RSAF Chong Pang Medical Centre} \hfill \textbf{Aug 2023 – Nov 2024} \\
\textit{Medical Sergeant cum Logistics-IC}
\begin{itemize}[noitemsep, leftmargin=*]
    \item Developed an Excel sheet to speed up stocktaking workflow and track indents/expiry dates.
    \item Created a Telegram bot for patients to find FAQs instead of calling landline.
\end{itemize}

\vspace{10pt}
\section*{PROJECTS}
\vspace{-5pt}
\textbf{Noteit – NUS Independent Software Development Project (Orbital)} \hfill \textbf{May 2025 – Aug 2025} \\
\textit{Full-Stack Academic Support Web App} – \url{https://note-it-drab.vercel.app/}
\begin{itemize}[noitemsep, leftmargin=*]
    \item Co-developed a full-stack app for note-sharing and Q\&A forums for NUS students.
    \item Engineered file upload with Supabase Storage, module-specific forum with tagging, custom PDF viewer with highlighting, and .ics calendar parser.
    \item Implemented error handling, edge-case checks, and conducted extensive user testing with NUS students.
    \item Paired programming, Git/GitHub tracking, deployed production build on Vercel.
\end{itemize}

\vspace{5pt}
\textbf{Task Manager Application} \hfill \textbf{Jan 2024 – Apr 2024} \\
\textit{JavaFX Chat-Based Task Manager} – \url{https://github.com/gnahuy123/jp}
\begin{itemize}[noitemsep, leftmargin=*]
    \item Built a comprehensive task-tracking chat app with GUI using JavaFX, with save/load, date/time handling, and search features.
    \item Executed advanced Git workflows, CI/CD pipeline, and collaborative development.
    \item Applied JUnit testing, CheckStyle, JavaDoc, achieving 95\%+ code coverage.
    \item Delivered production-ready JAR distributions with Gradle.
\end{itemize}

\vspace{5pt}
\textbf{Mommy.AI – Hack@SMU} \hfill \textbf{Mar 2024} \\
\textit{AI-Powered Productivity App with Personality}
\begin{itemize}[noitemsep, leftmargin=*]
    \item Designed and developed a React Native (Expo) app with authentication, task creation, calendar integration.
    \item Integrated local LLaMA 3.2 model via Ollama for on-device natural language parsing.
    \item Implemented personalised AI-driven notifications with Node.js/Express backend.
\end{itemize}

\vspace{5pt}
\textbf{Database Management for Restaurant – CS2102} \hfill \textbf{Aug 2025 – Nov 2025}
\begin{itemize}[noitemsep, leftmargin=*]
    \item Designed and implemented a PostgreSQL relational database schema from multiple CSV sources.
    \item Developed Python scripts to parse and clean data from 4 CSV files.
    \item Wrote and optimized SQL triggers to enforce business logic and data consistency.
\end{itemize}

\vspace{5pt}
\textbf{Driving Slot Booking Bot} \hfill \textbf{Oct 2023}
\begin{itemize}[noitemsep, leftmargin=*]
    \item Utilised Selenium to create a bot that snatches available booking slots.
\end{itemize}

\vspace{5pt}
\textbf{NBA Dashboard} \hfill \textbf{Dec 2024}
\begin{itemize}[noitemsep, leftmargin=*]
    \item Created dashboard using StreamLit to visualise team data for future games.
    \item Retrieved legacy data from 3rd-party API and scraped future schedules with Beautiful Soup.
\end{itemize}

\vspace{10pt}
\section*{ACHIEVEMENTS, LEADERSHIP \& COMMITTEE EXPERIENCE}
\vspace{-5pt}
\textbf{Project Grit – Head Teacher} \hfill \textbf{Jun 2025 – Jul 2025}
\begin{itemize}[noitemsep, leftmargin=*]
    \item Curated lesson plans and led 12 volunteers to teach Python fundamentals to children (10–12 years).
\end{itemize}

\vspace{5pt}
\textbf{ASRJC Choir – Assistant Student Conductor} \hfill \textbf{Apr 2020 – Apr 2021}
\begin{itemize}[noitemsep, leftmargin=*]
    \item Directed and conducted a 40-member choir, leading weekly rehearsals and performances.
    \item Answered queries during open house, contributing to 12\% increase in signups.
\end{itemize}

\end{document}